Openness and Computational Reproducibility in plant pathology: where do we stand and a way forward

### 2022-06-02 analysis/paper/paper.Rmd
Use new functions to import notes

rrpp <- import_notes()

opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  dev = c("postscript"),
  out.width = "100%",
  comment = "#>",
  dev = "cairo_pdf",
  cache = FALSE
)

ir <- import_interrater_scores()
```

>>>>

rrpp <- import_notes_paper()
ir <- import_interrater_scores_paper()

opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  dev = c("postscript"),
  out.width = "100%",
  comment = "#>",
  dev = "cairo_pdf",
  cache = FALSE
)
```
